Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-04-13 talk/icooolps2011/paper.tex
comments by rhy0lite

Conceptually, the significant speed-ups that can be achieved with
dynamic compilation depend on feeding into compilation and exploiting
values observed at runtime. In particular, if
there are values which vary very slowly, it is possible to compile multiple
specialized versions of the same code, one for each actual value.  To exploit
the runtime feedback, the implementation code and data structures need to be
structured so that many such slow-varying values are at hand. The hints that
we present allow exactly to implement such feedback and exploitation in a
meta-tracing context.

@@

@@

>>>>

Conceptually, the significant speed-ups that can be achieved with
dynamic compilation depend on feeding into compilation and exploiting
values observed at runtime. In particular, if
there are values which vary very slowly, it is possible to compile multiple
specialized versions of the same code, one for each actual value.  To exploit
the runtime feedback, the implementation code and data structures need to be
structured so that many such slow-varying values are at hand. The hints that
we present precisely allow us to implement such feedback and exploitation in a
meta-tracing context.

@@

\cfbolz{XXX also explain that some forwarding of guarded values is happening,
make clearer which figures show optimized code and which show non-optimized
code}

@@

XXX Peng Wu and David Edelsohn
